\subsection{Glycan Composition Network Smoothing}

    Ideally, each glycan present in a sample under analysis would produce sufficient
    experimental evidence that they can be identified. In practice, glycan
    compositions with lower abundances may not present strong evidence, leading
    to those glycan compositions being discarded. Others have demonstrated that
    it is advantageous to use relationships between glycans based on biosynthetic
    or structural rules to adjust the score of a single glycan assignment
    (\cite{Goldberg2009, Kronewitter2014}). To improve performance, we propose
    a method based on Laplacian regularized least squares (\cite{Belkin2006})
    to use evidence from glycan compositions related over a network to smooth
    its evaluation of glycan composition feature matching.

    % new material per reviewer request
    \reviewchange{
    Previous approaches to using information regarding identification of one
    glycan composition to increase the confidence in another have been proposed
    by} \cite{Goldberg2009} and \cite{Kronewitter2014} \reviewchange{using different techniques.
    Goldberg et al. used random walks along the biosynthetic network between identified
    glycan compositions to increase the confidence of those connected compositions. This
    method works well but requires that the parameters of the random walk be properly tuned
    for the biosynthetic network being used. Laplacian regularized least squares is more
    robust to small changes to the network and is able to use the entire network. Kronwitter
    et al. included a term in their criterion for detection requiring the presence of another
    glycan composition with one more or one less monosaccharide to permit identification. This
    puts substantial weight on a boolean term, giving it the ability to overrule other
    experimental evidence. Similar methods could be devised using methods like ant colony
    optimization to traverse the biosynthetic graph, or a a database-specific belief network,
    but these methods would require considerable manual tuning for each new database to be
    tested.}

    \input{methods/network_smoothing/graph_definition}

    \input{methods/network_smoothing/neighborhood_definition}

    \input{methods/network_smoothing/laplacian_regularization}

    % this section is far too long to include in the main text
    % so it is included in the supplement instead
    % \input{methods/network_smoothing/parameter_estimation}
