\subsection{Chromatogram Aggregation}
    We clustered peaks whose neutral masses were within $\delta_{mass} = 15$ parts-per-million error
    (PPM) of each other. When there were multiple candidate clusters for a single peak,
    we used the cluster with the lowest mass error. Next, we sorted each cluster by time,
    creating a list of aggregated chromatograms. To account for small mass differences,
    we found all chromatograms which were within $\delta_{mass} = 10$ PPM of each other and which overlap
    in time and merge them. These mass tolerances were selected empirically, and can be
    adjusted as needed by the user.

\subsection{Glycan Composition Matching}
    For each chromatogram, we searched each glycan database for compositions
    whose masses were within $\delta_{mass} = 10$ PPM for QTOF data, $5$ PPM
    for FTMS data. \reviewchange{These values are commonly used for data from these instruments
    based upon information from their manufacturers}. We merged all chromatograms
    matching the same composition. Then, for each mass shift combination \reviewchange{expected for
    each sample}, we searched each glycan database for compositions whose neutral
    mass were within $\delta_{mass}$ of the observed neutral mass - mass shift
    combination mass, followed by another round of merging chromatograms with the
    same assigned composition. We reduced the data by splitting each feature where the time
    between sequential observation was greater than $\delta_{rt} = 0.25$ minutes and
    removed chromatograms with fewer than $k = 5$ data points. The same chromatogram may be
    given multiple assignments and designated multiple mass shifts, and chromatograms
    without glycan assignments may use chromatograms with glycan assignments as mass shifted
    components. This ambiguity information was propagated through each merge and split step.
    We termed these remaining assigned and unassigned chromatograms \textit{candidate features}.
